Visualizing Functional Data

### 2016-11-01 main.tex
abstract, intro

\title{Visualizing Functional Data}
\author{Hannah Aizenman}
\committee{ Dr. Michael Grossberg(Advisor), Robert Haralick, Huy Vo}
\submitted{}
\abstract{}

\begin{document}
\makefrontmatter

@@

High dimensional data is catch-all term, typically used to describe data that's highly
multivariate or data that's structurally complex, or even data that simply has
a large number of observations. The lack of specificity of the phrase
`high-demensional` can make it difficult to parse out which high-dimensional
analysis and visaualization technique is suited to the research question at
hand. To answer that question, it's crucial to first have a set of working
definitions for discussing the data:

\begin{definition}
\item[measurements] criteria based assignment of numbers to objects or events \cite{grimm1993}
\item[variables] ``any characteristics, number, or quantity that can be measured
  or counted''\cite{ABS}

\item[field] dataset type where each cell has associated information \cite{munzner14ii}    
\end{defintion}

>>>>

\title{Visualizing Functional Data}
\author{Hannah Aizenman}
\committee{ Dr. Michael Grossberg(Advisor), Robert Haralick, Huy Vo}
\submitted{}
\abstract{There are an almost overwhelming number of machine learning and
  visualization techniques, but each technique makes some underlying
  assumptions about how the data is structured. While sometimes the
  observations are completely independent from each other, in many instances
  the observations are sampled from 1D continuum like time or 2d surface such
  as space.This survey uses functional data analysis to classify visualizations based on
  the number of variables, whether the variables are independent, and how the
  observations are related to each other}
\begin{document}
\makefrontmatter

@@

High dimensional data is catch-all term, typically used to describe data that's highly
multivariate or data that's structurally complex, or even data that simply has
a large number of observations. The lack of specificity of the phrase
`high-demensional` can make it difficult to parse out which high-dimensional
analysis and visaualization technique is suited to the research question at
hand. Datasets inherently have two components, the variables and the
observations of those variables. Functional data analysis provides a language
for formalizing the structure of the data in such a way that it clarifies the
possible interactions in the data.

%%paragraph on functional data analysis

Observations can often be reduced to one of the following forms:

\begin{tabular}
   & univarate   & bivariate                & multivariate \\
0D & v_i         & v0_i, v1_i               & v0_i, \dots, vn_i \\
1D & v_i(x_i)     & v0_i(x_i), v1_i(x_i)    & v0_i(x_i), \dots, vn_i(x_i)\\
ND & v_i(x0_i,\dots,xn_i)     & v0_i(x0_i,\dots,xn_i), v1_i(x0_i,\dots,xn_i)    & v0_i(x0_i,\dots,xn_i), \dots, vn_i(x0_i,\dots,xn_i)\\
\end{tabular}

The variables $v0,\dots, vn$ can also potentially be dependent on each other, adding in a third level of interactions that a visualization may want to caputure.
